---
title: "HW4_SDS315"
output:
  pdf_document: default
  html_document: default
date: "2024-02-13"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
options(scipen=999)
library(dplyr)
library(tidyverse)
library(mosaic)
library(ggplot2)
```

## HW 4

Name: Madeline Boss

EID: mrb5727

To see the code visit [Github](https://github.com/MadelineRBoss/HW4_SDS315)

```{r datasets, include = FALSE}
data1 <- read_csv("GasPrices.csv")
data2 <- read_csv("sclass.csv")
data3 <- read_csv("nbc_pilotsurvey.csv")
data4 <- read_csv("ebay.csv")
```

### Probelm 1

#### Theory A  

Claim: If there is no direct competition in sight, gas stations charge more  

Evidence:  

```{r 1A, echo =FALSE}
Competitors_average_change <- do(10000)*diffmean(Price ~ Competitors, data=mosaic::resample(data1))

Competitors_ci <- confint(Competitors_average_change, level = 0.95)

ggplot(Competitors_average_change) + geom_histogram(aes(x = diffmean), binwidth = 0.005) + labs(x = "avergae mean differnece in price", y = "frequency", title = "Average price difference between gas stations without competitors and gas stations with competitors")
```

Conclusion: In Summary, gas prices for gas stations for without nearby competitors have a price increase between \$`r round(Competitors_ci[2],4)` and \$`r round(Competitors_ci[3],4)` with 95% confidence. Since 0 is included in the confidence interval, we cannot say with 95% confidence that gas stations without competitors have a price increase.  

\newpage

#### Theory B  

Claim: The richer the area, the higher the gas price  

Evidence:  

```{r 1B, echo=FALSE}
ggplot(data1) + geom_point(aes(Income, Price)) + labs(title = "Income of an Area vs Gas Station Prices")

data1$Income <- data1$Income/10000

boot_income = do(10000)*lm(Price ~ Income, data=mosaic::resample(data1))

income_ci <- confint(boot_income, level = 0.95)
```

Conclusion: In summary, income and price has positive relationship, with an average increase between \$`r round(income_ci$lower[2], 4)` and \$`r round(income_ci$upper[2],4)` for every 10,000 dollars increased in mean income of the ZIP code the gas station is located, with 95% confidence. Since the confidence interval only has positive values, we can conclude with 95% confidence higher ZIP income does increase gas station prices.  

\newpage

#### Theory C  

Claim: Gas stations at stoplights charge more.  

Evidence:  

```{r 1C, echo=FALSE}
Stoplight_average_change <- do(10000)*diffmean(Price~Stoplight, data=mosaic::resample(data1))

Stoplight_ci <- confint(Stoplight_average_change, level = 0.95)

ggplot(Stoplight_average_change) + geom_histogram(aes(x = diffmean), binwidth = 0.005) + labs(x = "avergae mean differnece in price", y = "frequency", title = "Average price difference between gas stations at stoplights and gas stations not at stoplight")
```

Conclusion: In Summary, gas prices for gas stations for nearby stoplights have a price increase between \$`r round(Stoplight_ci[2],4)` and \$`r round(Stoplight_ci[3],4)` with 95% confidence. Since 0 is in the confidence interval, we cannot say with 95% confidence there is a price increase for stations nearby stoplights.  

\newpage

#### Theory D  

Claim: Gas Stations with direct highway access charge more.  

Evidence:  
```{r 1D, echo=FALSE}
#Fix Description
Highway_average_change <- do(10000)*diffmean(Price ~ Highway, data=mosaic::resample(data1))


Highway_ci <- confint(Highway_average_change, level = 0.95)

ggplot(Highway_average_change) + geom_histogram(aes(x = diffmean), binwidth = 0.005) + labs(x = "avergae mean differnece in price", y = "frequency", title = "Average price difference between gas stations at highways and gas stations not at highways")
```

Conclusion: In Summary, gas prices for gas stations next to highways have a price increase between \$`r round(Highway_ci[2],4)` and \$`r round(Highway_ci[3],4)` with 95% confidence. Since there's only positive values in the confidence interval, we can say with 95% confidence there is an price increase for gas stations near highways.  

\newpage

#### Theory E  

Claim: Shell charges more than all other non-Shell Brands.  

Evidence:  
```{r 1E, echo=FALSE}
data1E <- mutate(data1, "Is_Shell" = ifelse(Brand == "Shell", TRUE, FALSE))

Shell_average_change <-do(10000)*diffmean(Price ~ Is_Shell, data=mosaic::resample(data1E))

Shell_ci <- confint(Shell_average_change, level = 0.95)

ggplot(Shell_average_change) + geom_histogram(aes(x = diffmean), binwidth = 0.005) + labs(x = "avergae mean differnece in price", y = "frequency", title = "Average price difference between Shell gas stations and other gas stations")
```

Conclusion: In Summary, gas prices for Shell gas stations compared to other gas stations have a price increase of \$`r round(Shell_ci[2],4)` and \$`r round(Shell_ci[3],4)` with 95% confidence. Since the confidence interval has 0, we are not able to say with 95% confidence that Shell gas stations charge more.   

\newpage

### Probelm 2  

#### Part A  
```{r 2A, echo=FALSE}
data2A <- filter(data2, year == 2011, trim == "63 AMG")
boot_2a <- do(10000)*mean(~mileage, data=mosaic::resample(data2A))

ci_2a <- confint(boot_2a, level = .95)
```

The average mean mileage of used 2011 S-Class 63 AMGs with 95% confidence ranges from `r round(ci_2a[2],2)` and `r round(ci_2a[3],2)`.  

#### Part B  
```{r 2B, echo=FALSE}
data2B <- filter(data2, year == 2014, trim == "550")
data2B <- mutate(data2B, 'isBlack' = ifelse(color == "Black", "True", "False"))
boot_2b <- do(10000)*prop(~isBlack == "True", data=mosaic::resample(data2B))

ci_2b <- confint(boot_2b, level = 0.95)
```

The average proportion of black cars for 2014 S-Class 500 with 95% confidence ranges from `r round(ci_2b[2], 3)` and `r round(ci_2b[3], 3)`.  

\newpage

### Probelm 3

#### Part A  

Question: What show makes people happier: Living with Ed or My Name is Earl?

Approach: Bootstrap the average happiness score for each show and compare the difference in means (Living with Ed - My Name is Earl). Positive values represent Living with Ed making people happier, while negative values represent My Name is Earl making people happier.

Results:
```{r 3a, echo =FALSE}
data3A <- filter(data3, Show == "Living with Ed" | Show == "My Name is Earl")

Ed_vs_Earl <- do(10000)*diffmean(Q1_Happy ~ Show, data=mosaic::resample(data3A))

Ed_vs_Earl_ci <- confint(Ed_vs_Earl, level = .95)
```
The 95% confidence interval is `r round(Ed_vs_Earl_ci[2],3)` to `r round(Ed_vs_Earl_ci[3],3)`.

Conclusion: Since the confidence interval for difference in happiness includes 0, we cannot say with 95% confidence that either show makes people happier

#### Part B  

Question: Which show makes people more annoyed: The Biggest Loser or The Apprentice: Los Angeles.

Approach: Bootstrap the mean annoyed score for both The Biggest Loser and The Apprentice: Los Angeles and then compare the difference in means. Positive values means The Bigger Loser made people more annoyed, while negative values means The Apprentice: Los Angeles made people more annoyed.

Results:
```{r 3b, echo =FALSE}
data3B <- filter(data3, Show == "The Biggest Loser" | Show == "The Apprentice: Los Angeles")

Loser_vs_Apprentice <- do(10000)*diffmean(Q1_Annoyed ~ Show, data=mosaic::resample(data3B))

Loser_vs_Apprentice_ci <- confint(Loser_vs_Apprentice, level = .95)
```
The 95% confidence interval is `r round(Loser_vs_Apprentice_ci[2],3)` to `r round(Loser_vs_Apprentice_ci[3],3)`.

Conclusion: Since the 95% confidence interval has only negative values, we can conclude The Apprentice: Los Angeles makes people more annoyed.

#### Part C  

Question: What proportion of Americans find Dancing with the Stars confusing.

Approach: Bootstrap the proportion of results that responded a 4 or higher on Q2_Confusing.

Results:
```{r 3C, echo=FALSE}
boot_Dancing <- do(10000)*prop(~Q2_Confusing >= 4, data=mosaic::resample(filter(data3, Show == "Dancing with the Stars")))

Dancing_ci <- confint(boot_Dancing, level = .95)
```
95% Confidence Interval is `r round(Dancing_ci[2],4)` to `r round(Dancing_ci[3],4)`.

Conclusion: With 95% confidence, the proportion of Americans that are confused by Dancing with the Stars is between `r round(Dancing_ci[2],4)` and `r round(Dancing_ci[3],4)`.

\newpage
### Probelm 4  
```{r 4, echo=FALSE}
ad_differnce = do(10000)*diffmean(rev_ratio ~ adwords_pause,  data=mosaic::resample(data4))

ad_differnce_ci = confint(ad_differnce)
```

Question: Should Ebay stop paying for Google Ads?

Approach: Bootstrap the treatment group (pausing ads) and the control group (not pausing ads), and find the confidence interval for the difference in means in their revenue ratio. Positive numbers will show better revenue ratio for the treatment group, while negative values show the control group having a better revenue ratio.

Results: The 95% confidence interval is `r round(ad_differnce_ci[2],3)` to `r round(ad_differnce_ci[3],3)`.

Conclusion. Since the 95% confidence interval does not include 0 and contains only negative values, we can conclude that Ebay makes more money when they pay for Google ads.